---
title: "Ridge Regression"
author: "Clara Schartner and Araya Eamrurksiri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo=FALSE}
data("iris")
data("faithful")
```
## Ridge Regression
The Package `lab7` includes a function called `ridgreg` with which it is possible to do a ridge regression on data.
$\hat \beta^{ridge}=(X´X+ \lambda I)^{-1} X´y$ 
## Example
The use of the function is as can be seen below:
```{r}
library(lab7)
result<-ridgereg(eruptions~waiting,faithful)
result
```
## Further features
The function `predict` can be used to extract all predicted values.
```{r}
head(predict(result))
```
The function `coef` extracts all coefficients.
```{r}
coef(result)
```
And the function `print` prints both the formula used and the coefficients.
```{r}
print(result)
```

##Predictive
```{r}
library(mlbench)
library(caret)
data("BostonHousing")
intrain<-createDataPartition(BostonHousing$crim, p=0.75, list=FALSE)
training<-BostonHousing[intrain,]
testing<-BostonHousing

lm.s<-train(crim ~ .,data = training, method = "lm")
fore<-train(crim ~ .,data = training, method = "leapForward")

pre.fore<-predict(newdata=testing, fore)
confusionMatrix(data=pre.fore, testing$crim) #not working!! maybe because metric?
 plot(testing$crim,col="red")
 lines(pre.fore)
 
pre.lm<-predict(newdata=testing, lm.s)
confusionMatrix(data=pre.lm, testing$crim)

 #10foldcross <- trainControl(method = "repeatedcv", repeats=1)

             
```

